RCloud: Integrating Exploratory Visualization, Analysis and Deployment

### 2014-03-31 system.tex
UI overview

\todo{Edit}

\todo{View/Run/Share}

\todo{Call}

\todo{Browse/Search}. ``More like this'', and a custom webpage solely for browsing.

>>>>

The central of the screen is for editing code and visualizations through
the notebook interface. Supplementary ``asset'' files which are part of the
notebook but not part of the notebook flow, are edited on the right.
Controls at the top of the screen allow the user to quickly run, view, 
and share the notebook. The call mechanism is the URL itself; arguments are
read from the URL and the final cell is the result. On the left are the 
browsing area for seeing other users' notebooks and for searching, as well
as the help system.
